---
title: Shiny modules usage
author: Louis Le Nézet
date: '`r format(Sys.time(),"%d %B, %Y")`'
output:
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 2
header-includes: \usepackage{tabularx}
vignette: |
  %\VignetteIndexEntry{Shiny_modules_usage}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

    
Concept of shiny modules
==========================

Shiny modules are a usefull tool to decompose and organise complexe shiny app.
It also allowed to easily shared simple component across multiple apps or to 
share them with other people.
This is exactly the aim of this package, to provide simple but usefull unit of 
shiny modules for everybody to use.

As mentioned in the well written
[Shiny documentation](https://mastering-shiny.org/scaling-modules.html):

    "At the simplest level, a module is a pair of UI and server functions.
    The magic of modules comes because these functions are constructed in a
    special way that creates a “namespace”. So far, when writing an app, the
    names (ids) of the controls are global: all parts of your server function
    can see all parts of your UI. Modules give you the ability to create
    controls that can only be seen from within the module. This is called a
    namespace because it creates “spaces” of “names” that are isolated from
    the rest of the app."

Launching one of the shiny modules
==================================

All modules available in this package has at least one demo function for you to
experiment.
To launch it just add `_demo` to the module you want to test

```{r demo, eval=FALSE}
# For the plotHeatmap module
plotHeatmap_demo()
```

Add the shiny modules inside your app
=====================================

To add a module inside your application you will need to add the *ui* and the
*server* part of the module in each corresponding part of your app.
To do that you can follow the example below:

```{r app, eval=FALSE}
ui <- fluidPage(
  # Add the UI of data import
  dataImport_ui("datafile", "User data"),

  # Add the UI of plotHist
  plotHist_ui("hist"),

  # Add the UI of ggsaveBoth
  ggsaveBoth_ui("savehist")
)

server <- function(input, output, session) {
  # Add the serve of data import
  data <- dataImport_server("datafile")

  # Add the serve of plotHist
  my_plot <- plotHist_server("hist", df)

  # Add the server of ggsaveBoth
  ggsaveBoth_server("savehist", my_plot)
}
shinyApp(ui, server)
```

Thus in just a few line you've added 3 components that have independent
namespace and work together nonetheless.

## session_info
```{r sessionInfo, eval=TRUE}
sessioninfo::session_info()
```
